1.4: Data Visualization with ggplot2

### 2019-09-06 static/slides/04-slides.Rmd
Rescale slide images

@@

.center[
![](https://www.dropbox.com/s/e1nvb7x330c7ruk/aes2.png?raw=1)
]
]
---

@@

.left-code[
```{r plot-5, eval=F, echo=T}
ggplot(data = mpg)+
  aes(x = displ,
        y = hwy)+
  geom_point()+
  geom_smooth() #<<
```
]

@@

.center[
![](https://www.dropbox.com/s/gd9eisleu21lgga/goodfigure.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/k7fe3fpe6sc5oq7/ggplot2cheat.png?raw=1)
]

@@

- **R Studio's [ggplot2 Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)**
- **`ggplot2`'s website [reference section](https://ggplot2.tidyverse.org/reference/index.html)**
- STHDA's [be awesome in ggplot2](http://www.sthda.com/english/wiki/be-awesome-in-ggplot2-a-practical-guide-to-be-highly-effective-r-software-and-data-visualization)
- r-statistic's [top 50 ggplot2 visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
- Hadley Wickham's[ R for Data Science book chapter on ggplot2](http://r4ds.had.co.nz/data-visualisation.html)

>>>>

.center[
![:scale 90%](https://www.dropbox.com/s/e1nvb7x330c7ruk/aes2.png?raw=1)
]
]

@@

@@

.left-code[
```{r plot-5, eval=F, echo=T}
ggplot(data = mpg)+
  aes(x = displ,
        y = hwy)+
  geom_point(aes(color = class))+
  geom_smooth() #<<
```
]

@@

.center[
![:scale 70%](https://www.dropbox.com/s/gd9eisleu21lgga/goodfigure.png?raw=1)
]

@@

.center[
![:scale 55%](https://www.dropbox.com/s/k7fe3fpe6sc5oq7/ggplot2cheat.png?raw=1)
]

@@

- **R Studio's [ggplot2 Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)**
- **`ggplot2`'s website [reference section](https://ggplot2.tidyverse.org/reference/index.html)**
- Hadley Wickham's[ R for Data Science book chapter on ggplot2](http://r4ds.had.co.nz/data-visualisation.html)
- STHDA's [be awesome in ggplot2](http://www.sthda.com/english/wiki/be-awesome-in-ggplot2-a-practical-guide-to-be-highly-effective-r-software-and-data-visualization)
- r-statistic's [top 50 ggplot2 visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
